### 2022-09-20 main/chapter_context.tex
scribble some more notes

\paragraph{Measurement of known massive objects.}
Other than the Higgs boson, the heavy Standard Model resonances are the
$W$ and $Z$ bosons and the top quark, all of which are produced at
high rates by LHC proton-proton collisions.

The goal of measuring these heavy objects puts more emphasis on determining
the total energy of hadronic jets than their precise hadronic compositions.

@@

\paragraph{Design.}
Atlas is a Titan.
On the \cern\ Large Hadron Collider (LHC), \atlas\ is the largest detector
experiment, and alongside its majors neighbours
\cms~\cite{cms2008experiment},
\lhcb~\cite{lhcb2008experiment},
and ALICE~\cite{alice2008experiment}
it is a multi-kilotonne beast,
and a wonder of scientific engineering~\cite{
atlas2008experiment,
atlas1999design1,
atlas1999design2
}.

>>>>

\paragraph{Measurement of known massive objects.}
\TODO{
Argument:
want to measure W, t,
so measure jets and precise objects
so weaker B and heavy ion programme.
...
Refer to competitive measurements of W and t masses
and xsec of various rare processes (diboson, triboson)
}

Other than the Higgs boson, the heavy Standard Model resonances are the
$W$ and $Z$ bosons and the top quark, all of which are produced at
high rates by LHC proton-proton collisions.

The goal of measuring these heavy objects puts more emphasis on determining
the total energy of the hadronic jets produced by their hadronic decays
than precise hadrons that those jets comprise.

@@

\TODO{
Decay to SM particles,
emphasis on missing transverse momentum.
...
Many SUSY searches, many other exotics searches, no convincing evidence for
new effects.
}

\subsection{Design}
Atlas is a Titan.
On the \cern\ Large Hadron Collider (LHC), \atlas\ is the largest detector
experiment, and alongside its majors neighbours
\cms~\cite{cms2008experiment},
\lhcb~\cite{lhcb2008experiment},
and ALICE~\cite{alice2008experiment}
it is a multi-kilotonne beast,
and a wonder of scientific engineering~\cite{
atlas2008experiment,
atlas1999design1,
atlas1999design2
}.
